% !TEX root = Vorlage_EN.tex
\section{Background}
Increasing adoption in cryptocurrencies is a phenomenon that has gained great attention over the last couple of years. Since at least 2017 Bitcoin and blockchain technology became a hyped topic and focus of many industries and investors. With a cashflow of hundreds of billions of dollars (Firmen fangen an in Bitcoin un Co. zu investieren, sowie auch in eigene Tokens). Considering the blockchain technology and cryptocurrencies in general as a megatrend, several industries are influenced and forced to respond to this new technical challenge. Companies which are implementing blockchain related applications or exchanges gaining competitive advantage in the business environment. However, they became buzzwords which use is taken out of context frequently. (drin lassen?). (Vielleicht hier diese absurden beispiele wie mit dem Fahrradladen bringen, damit man sieht wie gehyped und komplex/ unverständlich das Thema anfangs für viele war).
(Jetzt eher so auf die Regierungen eingehen: viele Restriktionen, aber auch Offenheit, irgendwas über die federal reserved irgendwas :D und wie sich das ganze auswirken könnte. Dass das ganze schwierig ist ). 
It gets down to an increasing demand in cryptocurrencies. Making a fast buck becomes a simple procedure little knowledge about finance and blockchain presupposed. Today’s society is becoming more and more attentive to this topic through news, talk-shows, social media et cetera.
Although blockchain technology is already known since the early 1990’s. With the Bitcoin Whitepaper released in 2009 it became popular and a revolution for the financial system (vielleicht noch hier warum revolution: weil probleme der dezentralität gelöst wurden etc.). Blockchains and cryptocurrencies are an opportunity for a lot of innovation in this and many other fields. An easy accessibility for both users and creators, a trustless network, privacy, new approaches of access management, possibilities of participation in governance processes of some protocols and the possibility of the reversal of inflation to name a few.
Nowadays it is not necessary to install one’s wallet through the command line anymore. Applications like Metamask makes it easy to administer one’s crypto currencies in a pretty simple way as well as financial products like … (einfachstes product zur veranschaulichung was gut nutzbar ist [Pancake oder BIFI wollte ich hier nicht erwähen, weil die ja noch später kommen c: ]). These products are based on so-called smart contracts which are holding their program code and which are stored directly on the blockchain itself so that its integrity is assured/save/immutable (vielleicht rausstreichen). 

